---
title: "Financial Analytics"
author: "Avireddy Rohan"
date: "11/11/2021"
output: html_document
---

## Name: Avireddy NVSRK Rohan
## regno: 19BCE1180
### DATASET LINK:https://www.kaggle.com/sethirishabh/finance-company-loan-data?select=test_lAUu6dG.csv 

#### Dream Housing Finance company deals in all home loans. They have presence across all urban, semi urban and rural areas. Customer first apply for home loan after that company validates the customer eligibility for loan.


```{r pressure, echo=FALSE}
data=read.csv("train_loan.csv")
str(data)
```
```{r}
#library(ggplot2)
```
```{r}
#library(dplyr)
```

### DATA CLEANING PHASE
```{r}
dim(data)
```
```{r}
data=na.omit(data)
```

```{r}
head(data,10)
```
```{r}
table(data$Self_Employed)
```

```{r}
data$Dependents[data$Dependents=="3+"]=3
data$Self_Employed[data$Self_Employed==""]="No"
```

### visualizing number of self emp
```{r}
ed_fac=factor(data$Education,levels = c("Graduate","Not Graduate"))
ggplot(data,aes(x=Self_Employed))+geom_bar(color="white",fill="blue")+labs(title = "Distribution of self employed people",y='frequency')+facet_wrap(ed_fac,ncol=1)
```


```{r}
summary(data)
```

### creating a third column for total income of applicant and co applicant
```{r}
data <- data%>%
        mutate(total_income=ApplicantIncome+CoapplicantIncome)
```




```{r}
cor.test(data$total_income,data$LoanAmount)
```

### inference: since p value is less than 0.05 we can reject null hypothesis and we can say that there is a relationship between total income of applicant and their loan amount

### Logistic regression model
```{r}
#install.packages("ISLR")
```
```{r}
#library(ISLR)
```
### Encoding the predictors and label column
```{r}
#install.packages("superml")
```
```{r}
#library(superml)
```

```{r}
le=LabelEncoder$new()
data$Gender=le$fit_transform(data$Gender)
data$Married=le$fit_transform(data$Married)
data$Dependents=le$fit_transform(data$Dependents)
data$Education=le$fit_transform(data$Education)
data$Self_Employed=le$fit_transform(data$Self_Employed)


```
```{r}
data$Property_Area=le$fit_transform(data$Property_Area)
data$Loan_Status=le$fit_transform(data$Loan_Status)
```

```{r}
#library(caret)
```

```{r}
set.seed(123)
train_labs <- data$Loan_Status %>%
  createDataPartition(p=0.8,list=FALSE)
head(train_labs)
```
```{r}
train_data <- data[train_labs,]
test_data <- data[-train_labs,]
```
```{r}
train_data
```

```{r}
glm.fit <- glm(Loan_Status ~ Gender + Married + Dependents + Education + Self_Employed + LoanAmount+Credit_History+Property_Area+total_income, data = train_data, family = binomial)
```

```{r}
summary(glm.fit)

```

```{r}
glm.probs <- predict(glm.fit,
                    newdata = test_data,
                    type = "response")
```

```{r}

glm.pred <- ifelse(glm.probs > 0.5, 1, 0)
```

```{r}
glm.pred
```