---
title: "DATAFRAMES_LAB2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Name: Avireddy NVSRK Rohan
### Reg.no: 19BCE1180

##SECTION 2A
1. Create a data frame by considering 5 students and 4 courses (C1,C2, C3, C4). Each score has a maximum score of 30. If a student is absent for CAT1 of a course, the mark entry is 0 for that course. (Have 0 entry also in the data)

```{r}
names=c("JOHN","SARAH","SAM","CHARLES","JAMES")
C1=c(25,0,28,29,24)
C2=c(0,22,28,26,20)
C3=c(21,20,25,22,26)
C4=c(24,29,28,28,30)
stud=data.frame(names,C1,C2,C3,C4)
```
2. View the contents of the data frame.
```{r}
stud
View(stud)
```
3. Find the total marks of each student.

4. Append a column to include the total marks of the students and view the data frame.
```{r}
stud$total=rowSums(stud[c(2:5)])
stud
```
5. Find the maximum total marks and display the name of the participant who scored it.
```{r}
stud$names[which.max(stud$total)]

```
6.Compute the average mark in each course and append it as a new row in the data frame.
```{r}

stud <- rbind(stud,data.frame(names="average",C1=mean(stud$C1),C2=mean(stud$C2),C3=mean(stud$C3),C4=mean(stud$C4),total=mean(stud$total)))
stud

```
Store the details in a comma separated values (csv) file. Also suppress the row numbers.
```{r}

getwd()
write.csv(stud,"marks.csv",row.names = FALSE)

```
##INDEXING AND SLICING
8. Read the content of recently stored csv file in a data frame and view it.
```{r}
my_df=read.csv("marks.csv")
my_df

```
9.Access the marks of students in C2 using the column name.
```{r}
my_df$C2
```
10. Use index number to retrieve the same data.
```{r}
my_df[,3]
```
11.Extract the marks of third student in C3.
```{r}
my_df[3,4]
```
12. Extract the marks of the first and second student in all courses.
```{r}
my_df[c(1,2),]
```
13. Display the names and total marks of all students.
```{r}
my_df[,c(1,6)]
```
14. Make the column “name” as the row index of the data frame.
```{r}
row.names(my_df) <- my_df$names
my_df
```
15. Display the names of the students who were absent for the course C3 during CAT1
```{r}
temp <-my_df
boolv <- temp["C2"]==0
row.names(temp)[boolv]
```
16. Obtain the names whose total marks is below its average.
```{r}
bool1 <- temp["total"]<mean(temp$total)
row.names(temp)[bool1]
```
##Ex-2b Basic Operations in data frame
1. Install the package MASS
```{r}
#install.packages("MASS")
```
OUTPUT FOR Q1:WARNING: Rtools is required to build R packages but is not currently installed. Please download and install the appropriate version of Rtools before proceeding:

https://cran.rstudio.com/bin/windows/Rtools/
Installing package into ‘C:/Users/rohan/OneDrive/Documents/R/win-library/4.0’
(as ‘lib’ is unspecified)
trying URL 'https://cran.rstudio.com/bin/windows/contrib/4.0/MASS_7.3-54.zip'
Content type 'application/zip' length 1189557 bytes (1.1 MB)
downloaded 1.1 MB

package ‘MASS’ successfully unpacked and MD5 sums checked

The downloaded binary packages are in
	C:\Users\rohan\AppData\Local\Temp\Rtmpi4IuXC\downloaded_packages
	
2.Import the package MASS.
	
```{r}
library("MASS")
```
3. Display the structure of the data survey.
```{r}
data("survey")
survey_data=survey
str(survey_data)
```
4. Check the class and type of the data set survey in MASS.
```{r}
class(survey_data)
typeof(survey_data)
```
5. Get the number of rows and columns of the survey data frame.
```{r}
nrow(survey_data)
ncol(survey_data)
```
6.Get the dimension of the survey data frame.
```{r}
dim(survey_data)
```
7. Provide the statistical summary of the data frame.
```{r}
summary(survey_data)
```
8. Display the column names of the survey data frame
```{r}
names(survey_data)
```
9. Retrieve the top 3 rows from the data frame.
```{r}
head(survey_data,3)
```
10. Extract the bottom 2 rows from the data frame.
```{r}
tail(survey_data,2)
```
