---
title: "Ex1 Basic Data Types"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Name: Avireddy NVSRK Rohan
### Reg.no: 19BCE1180

## Question 1

Assign a numeric value to a variable ‘a’ and convert ‘a’ into an integer

```{r}

s1="assigning a numeric value to a"
s2="converting a to an integer"
s1
a = 15
class(a)
s2
a=as.integer(a)
class(a)
```
## Question 2

 Make this quote into an R string
– “Do you think this is a game?”, he said. “No, I think Jenga’s a game”, Archer 
responded.


```{r}
string='“Do you think this is a game?”, he said. “No, I think Jenga’s a game”'
print(string)
noquote(string)
```
## Question 3

Create two numeric vectors p & q

```{r}
p=vector(mode="numeric",length(3))
q=vector(mode="numeric",length(3))
p=c(1,2,3)
q=c(4,5,6)
p
q
class(p)
class(q)

```
## Question 4

Use R as a calculator to do basic arithmetic operations on p &q and store each result 
in different variables.

```{r}
sum=p+q
prod=p*q
div=p/q
sub=p-q

```
## Question 5

Calculate sqrt(a) and perform log2 transformation on the result.

```{r}
a
log(sqrt(a),2)
```
## Question 6

Calculate the 10-based logarithm of 100 and multiply the result with cosine of π.


```{r}
l=log(100,10)
l*cos(pi)
```
## Question 7

Create a vector ‘x’ using : operator from -2 to 2.


```{r}
x=vector("numeric")
x=c(-2:2)
x
```
## Question 8

Print the dimension and length of x.

```{r}
dim(x)
length(x)
```
## Question 9

Create two vectors small and caps with last 5 alphabets in lower case and first 5 
alphabets in upper case respectively. Bind it row and columnwise.


```{r}
small=vector("character",length=10L)
caps=vector("character",length=10L)
small=c("A","B","C","D","E","f","g","h","i","j")
caps=c("K","L","M","N","O","p","q","r","s","t")
r=rbind(small,caps)
c=cbind(small,caps)
r
c

```
## Question 10

 Create a matrix M=
1 2 5
−4 8 6
3 −1 7
 and find MxMxM.

```{r}
M=matrix(c(1,2,5,-4,8,6,3,-1,7),3,3,byrow = TRUE)
M
mp=M%*%M%*%M
mp
```
## Question 11

 Find the result of elementwise multiplication of M by M.


```{r}
M*M

```
## Question 12

 Find the transpose, inverse and determinant of M.

```{r}
print("inverse")
solve(M)
print("transpose")
t(M)
print("determinant")
determinant(M)
```

